\chapter*{ \begin{center} 
    \textbf{\LARGE ABSTRACT}  % Large, bold, and centered heading  
\end{center} }  
\addcontentsline{toc}{chapter}{ABSTRACT}  
\vspace{-2cm}  % Adjust this value if needed to reduce space further  
 

 The Medora Hospital Management System is a comprehensive web-based application developed to automate and manage hospital operations efficiently. The system integrates key departments—including Administration, Reception, Doctors, Pharmacy, Laboratory, and Patient Services—into a centralized and secure digital platform. It replaces traditional manual processes with a structured computerized system, thereby improving operational efficiency, reducing errors, and enhancing overall patient care.
\\\\
The application implements role-based access control to ensure secure interaction among users such as Admin, Receptionist, Doctor, Patient, Pharmacist, and Lab Staff. The Reception module manages patient registration, appointment scheduling, and billing. Doctors conduct consultations, generate digital prescriptions, and request laboratory tests. Lab staff upload test results electronically, while pharmacists manage medicine inventory and dispensing processes.
\\\\
A key feature of the system allows patients to register and purchase medicines directly from the pharmacy without mandatory doctor consultation. Patients can upload external prescriptions, which are verified and processed by the pharmacist. This enhances flexibility while maintaining proper medication tracking and control.Developed using the Laravel framework with a MySQL database, the system ensures data security, scalability, and high performance. By centralizing workflows and digitizing medical records, the Medora Hospital Management System significantly improves administrative efficiency and supports modern healthcare management practices.\\\\

