\chapter{APPENDIX}

\section{Minimum Software Requirements}

\medskip
\textbf{Operating System}: Windows 10/11, macOS, or Linux
\\\\
\textbf{Web Browser}: Google Chrome, Mozilla Firefox, or Microsoft Edge (latest version recommended)
\\\\
\textbf{Backend Framework}: Laravel 12
\\\\
\textbf{Programming Language}: PHP 8.2 or higher
\\\\
\textbf{Database}: MySQL 8.0 or higher
\\\\
\textbf{Web Server}: PHP Built-in Development Server, Apache, or Nginx
\\\\
\textbf{Dependency Managers}: Composer (for PHP packages), NPM (for frontend JavaScript assets)
\\\\
\textbf{Build Tool}: Vite 7 (for compiling and bundling frontend assets)
\\\\
\textbf{Mail Service}: Gmail SMTP (requires a Gmail App Password for OTP and notification emails)
\\\\
\textbf{Development Tools (Optional)}: Visual Studio Code, Git, Postman

\section{Minimum Hardware Requirements}

\textbf{Processor}: Intel Core i3 / i5 (or AMD equivalent) or higher for smooth server performance.
\\\\
\textbf{RAM}: 4 GB minimum (8 GB recommended for comfortable development with multiple services running).
\\\\
\textbf{Storage}: At least 500 MB free disk space for project files, vendor dependencies, and database storage.
\\\\
\textbf{Display}: 1366x768 resolution or higher for proper dashboard interface rendering.
\\\\
\textbf{Input Devices}: Keyboard, mouse, and a functional web camera (required for voter photo capture during vote casting).
\\\\
\textbf{Network Connectivity}: Stable internet connection required for OTP email delivery via Gmail SMTP. Local network is sufficient for system navigation.
\\\\

\section{Default System Credentials}

The following credentials are seeded into the system by the \texttt{DatabaseSeeder} and should be changed before any production deployment:

\medskip
\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Role} & \textbf{Email} & \textbf{Password} \\
\hline
System Administrator & admin@example.com & password \\
\hline
\end{tabular}
\caption{Default Seeded System Credentials}
\label{tab:credentials}
\end{table}

BLO accounts are created manually by the administrator through the Admin Dashboard. Voter and Candidate accounts are created through their respective public registration forms.
