\chapter*{  \begin{center}
    \textbf{\LARGE ACKNOWLEDGEMENT}  % Large, bold, and centered heading  
\end{center} }  
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENT}  
\vspace{-2cm}  % Adjust this value if needed to reduce space further  
 
\noindent
With heartfelt gratitude, I extend my deepest thanks to the Almighty for His unending grace and blessings that have guided me throughout this endeavour. His presence has been a constant source of strength and inspiration.
\\\\
I am profoundly grateful to Dr. Bindiya M Varghese, Dean, Department of Computer Science, and Mr. Ajay Antony Joseph, Faculty Guide, for their invaluable mentorship, timely advice, and constant encouragement. Their guidance was instrumental in shaping the direction and outcome of this project, and their constructive feedback enabled me to develop a structured, functional, and academically sound system.
\\\\
I sincerely thank all the faculty members of the Department of Computer Science, RCSS, for their continued support and motivation throughout my academic journey. Their teaching and insights have greatly contributed to my technical and analytical growth.
\\\\
I extend my heartfelt appreciation to my parents and family, whose unwavering moral support and encouragement made this project possible. I am also grateful to my friends and classmates, whose collaborative spirit and assistance at every step made this work a fulfilling experience.
\vspace{1cm}
\begin{flushright}
\textbf{Mathew Titus}
\end{flushright}
